Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-03-01 paper.tex
adicionados apontamentos do chu e anotacoes minhas enviadas de volta com a revisao

\section{Conclusions}
The characterization of interaction networks resulted from stability observations. Along temporal activity statistics, this work reports the stability of the principal components (in the concentration of dispersion and composition) and of the ternary partitioning (periphery, intermediary, hubs) relative sizes, evident in the comparison with the Erd\"os-R\'enyi model. These results suggested typologies for both agents and the networks.

    \subsection{Further work}
The task of delivering a first and general characterization of chosen interaction networks involved a larger effort. The different aspects covered requires not only different analytical background, but also considerations about textual production and social psychology. These are receiving attention within dedicated works and are summarized in this section.

        \subsubsection{Constancy of general characteristics eases tipologization}

Regarding topological aspects of interaction networks, further work should inspect other measures in each of the three connective sectors: hubs, intermediary and periphery.

Observance of attributes with greater contribution to principal components of LDA should reveal best chances to present these three sections as clusters in the network measurements space. Another possibility, specially for a brute-force characterization of such sectors, is to remove vertices with degree close to $k_1$ or $k_2$ depicted in figure~\ref{fig:setores}. The subtraction $\widetilde{P}(k)-P(k)$ (see Section~\ref{subsec:typ}) results in two positive clusters for periphery and hubs, and a negative cluster for intermediary vertices. This might support classification of the three sectors by clustering, a more traditional approach to classification.

Observed networks were coherent with literature in different aspects, such as concentration of activity, and clusterization versus connectivity patterns. Even so, analysis of data from other virtual environments, such as Facebook, Twitter and LinkedIn, might help understanding how general are these structures and what are convenient uses.

A paired article is dedicated to textual production of the network sectors~\cite{rcText}. Resulting knowledge purposes networks and participants typologies, and both topological and textual analysis should foster characterization of interaction networks and participation incidences.
Stability reported in this article eases tipologization of outliers and more usual participation patterns. See Section~\ref{sec:related} for the consideration of works related to presented results.

        \subsubsection{Results exploitation}
On the technological trend, usage of such characteristics are taking place in linked data and electronic government technologies~\cite{ops,opa,ensaio}. Further steps involve elaboration and tests of social dynamics that takes advantages of these results. These results are also being used for anthropological physics experiments~\cite{anPhy} and knowledge acquisition~\cite{rcText}.

>>>>

\section{Conclusions and further work}
The characterization of interaction networks resulted from stability observations. Along temporal activity statistics, this work reports the stability of the principal components (in the concentration of dispersion and composition) and of the ternary partitioning (periphery, intermediary, hubs) relative sizes, evident in the comparison with the Erd\"os-R\'enyi model. These results suggested typologies for both agents and the networks.

%    \subsection{Further work}
The task of delivering a first and general characterization of chosen interaction networks involved a larger effort. The different aspects covered requires not only different analytical background, but also considerations about textual production and social psychology. These are receiving attention within dedicated works and are summarized in Section~\ref{sec:related}.

%        \subsubsection{Constancy of general characteristics eases tipologization}

Regarding topological aspects of interaction networks, further work should inspect other measures in each of the three connective sectors: hubs, intermediary and periphery.
Observance of attributes with greater contribution to principal components of LDA should reveal best chances to present these three sections as clusters in the network measurements space. Another possibility, specially for a brute-force characterization of such sectors, is to remove vertices with degree close to $k_1$ or $k_2$ depicted in figure~\ref{fig:setores}. The subtraction $\widetilde{P}(k)-P(k)$ (see Section~\ref{subsec:typ}) results in two positive clusters for periphery and hubs, and a negative cluster for intermediary vertices. This might support classification of the three sectors by clustering, a more traditional approach to classification.

Observed networks were coherent with literature in different aspects, such as concentration of activity, and clusterization versus connectivity patterns. Even so, analysis of data from other virtual environments, such as Facebook, Twitter and LinkedIn, might help understanding how general are these structures and what are proper uses.

        \subsection{Results exploitation}
A paired article is dedicated to textual production of the network sectors~\cite{rcText}. Resulting knowledge purposes networks and participants typologies, and both topological and textual analysis should foster characterization of interaction networks and participation incidences.
Stability reported in this article eases tipologization of outliers and more usual participation patterns (see Sections~\ref{sec:related} and~\ref{sec:pty}).

On the technological trend, usage of such characteristics are taking place in linked data and electronic government technologies~\cite{ops,opa,ensaio}. Further steps involve elaboration and tests of social dynamics. These results are also being used for anthropological physics experiments~\cite{anPhy}.
